\documentclass[a6paper]{article}
\usepackage[margin=5mm]{geometry}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\usepackage[most]{tcolorbox}
\usepackage{ulem}
\usepackage[sf,bf,big,raggedright,compact]{titlesec}	% change section color to blue
% \usepackage[backend=biber,bibstyle=authoryear,citestyle=../authoryearbrack]{biblatex}

\ifdefined\chinchin
\usepackage[CJKspace]{xeCJK}
\setCJKmainfont[BoldFont=SimHei,ItalicFont=AR PL KaitiM GB]{SimSun}
\newcommand{\cc}[2]{#1}
\else
\newcommand{\cc}[2]{#2}
\fi


%\setlength{\headheight}{0cm}
%\setlength{\hoffset}{0cm}
%\setlength{\topmargin}{-2cm}
%\setlength{\oddsidemargin}{-2cm}
%\setlength{\evensidemargin}{-2cm}
%\setlength{\textwidth}{20cm}
%\setlength{\textheight}{26cm}
%\setlength{\headsep}{0cm}
%\setlength{\topskip}{0cm}
%\setlength{\footskip}{0.9cm}  % between bottom of page and page number
%\setlength{\floatsep}{0cm}
%\setlength{\textfloatsep}{0.6cm}
%\setlength{\intextsep}{0.5cm}
%\setlength{\parindent}{0em}   % em = width of capital M

\setcounter{secnumdepth}{2}		% no section numbers

\titleformat{\section}[hang]{\LARGE}{}{0pt}{}
% \titleformat{\subsection}[hang]{\bfseries\large\color{blue}}{\thesubsection \hspace{5pt}}{0pt}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2.8ex plus0.8ex minus0.8ex}

\begin{document}
	
\title{The Woman with The Flying Head \\
{ \small (Kubi no Tobu onna (1985))}
}
\author{by KURAHASHI YUMIKO (倉橋 由美子)}
\date{}

\large
\maketitle
%\vspace{-3cm}

My father had a high-school classmate who was a little
out of his mind.  I never met him in person, only heard
stories.  Let me call him Mr.  K for now.  It was several
days before my father died of a stroke that he told me
about Mr. K's secret.  (I wonder if the timing was pure
coincidence.)  This is not to say that Mr. K himself had
hidden something from people; all his acquaintances knew
about this “secret.”  It is just that my father had kept it
secret from me till then.

This is a rough outline of the story.

I heard that since he had come home from China after the
Japanese retreat, K had been repeatedly admitted to a
mental institution and discharged.  One day I ran into him in the
street, and somehow or other it was decided that he should
come to visit me at home someday.  There is a legend that a
scholar of the old school called Hyakken posted two verses
at the entrance of his house.  One was Ota Nanpo's “Receiving
guests is what troubles me most / But not if the guest is
you.”  The other was a spoof of the ﬁrst: “Receiving guests
is what delights me most / But not if the guest is you.”
Well I don't quite have the nerve to post the latter poem,
but honestly, a visit from someone like K was about the
least delightful thing I could think of.  I did try to convey to
him how unwelcome he would be, but K, a rather abnormal
man, soon came for his visit.  I remember this was before
you were born.

Let me make it clear that K did not at all appear to be
mad;  there was nothing unsettling about his gaze, for
example.  It is true that he was gaunt and dressed like a vagrant,
but that was not unusual in postwar Japan.  But one could
not help noticing the big, expensive-looking leather club
bag he always carried in town.  He had it with him when he
came over to my house.

We talked about nothing in particular for a while, then he
abruptly changed the subject.

“Do you know about the people with fantastic shapes
described in the Chinese Classic of Mountains and Seas (山海經)
and The Account of Seeking Spirits (搜神记)?”

“The only ones I know about are the tribe of three-
headed folk, the hairy people who were forced to work on
the Great Wall, the giant who could swallow three thousand
ogres—”

“You know them well.  I am impressed! Among those
strange tribes were the Aborigines with ﬂying heads.”

“Never heard of them.”

“Their heads would leave their bodies and ﬂy around in
the middle of night.”

“What a peculiar afﬂiction.”

“It was not an afﬂiction that particular individuals suffered
from.  Everyone in the tribe, old or young, male or
female, was like that.  By the way, are you still single?”

“I got married last year.  My wife has been out since
yesterday, visiting her parents on some family business.”

“I lived with a woman too.”

“Why in the past tense?”

“This `woman' was actually a seventeen-year-old girl.
You know the one, the Chinese-looking girl, the one I
brought home --- or who followed me.”

“I remember.  Once you washed off the dust, she turned
out to be an unearthly beauty.”

“Well, eventually she grew up.”

“That's only natural.   I see, you became a Prince Genji,
who slept with Murasaki, whom he had adopted and
raised.”

I made this joke having forgotten that K was out of his
mind.   But K did not seem offended; he just kept smiling,
his indescribably sorrowful eyes like the winter sun.
“We couldn't get married.   Li was my legally adopted
daughter.   Still, I sneaked into her bedroom one night.  For
some reason, she had wanted to sleep alone ever since she
had been little, so we had always slept separately.  Imagining
what a sweet expression would be on her face while she
slept, I couldn't resist the desire to visit her.  Telling myself
that I would be just looking at her face, I peeped into the
chamber --- to ﬁnd she had no face.”

“No face?”

“She had no head.  I went completely pale, assuming that
she had been murdered.  Then I realized there was no blood.
Moreover, even without a head her body seemed alive;  her
well-shaped breasts moved up and down, though I didn't
know how she could breathe without a head.  Between her
breasts she was shiny with sweat.  But still, she had no
head.”

“So she was one of the Aborigines with ﬂying heads."

“You don't seem too surprised.”

“Of course I am.”

I was careful to try not to excite this mentally unstable
man, for his story seemed to be coming to its climax.
“I was astonished.  I was confused.  All the same, I knew
feelings beyond all morality had been aroused.  My head felt
overheated.  Li was alive without her head, without consciousness
or intellect.  I touched her hand, which was warm
and soft.  It grew sweaty while I was grasping it.  Beneath
the quilt her legs were slightly parted.  Li's legs were different
from any Japanese woman's, long and straight, with feet
as exquisite as ivory carvings.

“Nothing happened that night.  Li was as good-humored
as ever in the morning.  There was nothing to suggest the
extraordinary incident of the previous night.  The next night
it was the same thing --- no development.  Apparently, Li herself
did not know that her head would leave her body and
fly away.  If she had known, she could have tied it down so
that it couldn't ﬂy away.”

“Couldn't she tell if she had been molested while her
head was away?"

“Her head couldn't tell, of course.  Her body must have
known, though.  One night I ﬁnally lay with the headless Li.
After that I had sex with her every night.  Her headless body
was like a sleeping body; it reacted vaguely when I touched
it.  In time, it seemed to learn a sense of pleasure; the movements
of our bodies became well coordinated.  One night
Li's body shuddered in a different way, and her limbs
coiled around me, clasping me terribly tightly.  I nearly
screamed in terror; I wondered if her head had come back
and Li's pleasure was completed, or if some monster of
carnal desire was trying to squeeze me to death.  But I came
back to my senses to ﬁnd she still had no head.  As always,
the surface of her neck felt like a wet lip.  I discovered that
the headless body would surge with pleasure if I licked the
wet part.  Li's head never seemed to know anything about
this.  Her body was unable to inform her head of its nightly
experiences.”

“Where did her head ﬂy every night?” I cut in.  I could
not bear to let him go on like this.

“Speaking of her head ....” K snickered weirdly.

It is not pleasant to hear a lunatic snicker that way.  “Her
head didn't by chance visit a secret lover through the passage
of dreams every night?” I said, trying to get him to
finish the thought.

“You won't believe this.  One day, with a serious expression,
Li confessed to me, 'Father, I have fallen in love with
someone.  I dream of secretly visiting him every night.'  Of
course it wasn't me she was in love with.”

“And you were overwhelmed with jealousy?”

“It's not that simple.  I felt like any father of a grown-up
daughter, or like Prince Genji when Tamakazura, one of his
adopted daughters, was taken away by General Higeguro.

But honestly, I felt like saying to her, `Is that so?  Well,
you've grown up and now you love someone.  Go, get out of
here and marry him.  But leave your body here.  Only your
head is allowed to go.' ”

“That's terrible.”

“I didn't actually say that to her.  All the same, Li began to
cry.  `I can't marry him,' she said.  `He's already married.' ”

I felt I couldn't stand to listen any longer.  Once more I
urged him to ﬁnish the story.

“You are right,” he concluded.  “I was as jealous as anyone
in such a position.  One night, in a fit of jealousy, I did a
terribly stupid thing.  Toward dawn, Li's head came home
from meeting its lover.  For the ﬁrst time I saw it fly: it ﬂew
like a big bee, using its ears as wings --- I hear that's how the
heads of the Aborigines with ﬂying heads flew.  Her head
looked excited and joyful, and this enraged me.  In an instant,
I covered her body with the sheet so her head couldn't
reattach itself.  Her head looked distressed and fluttered
about, but it did not ask me for forgiveness.  It seemed in
agony.  `Look at yourself --- you deserve it!' I thought.  Before
long, Li's head stopped breathing.”

“How could you be so cruel!”

“I know, but by the time I felt regret for what I had done,
it was already too late.  Almost instantaneously, Li's head
grew dry, wrinkled, and shrank to an incredibly small size.
Here it is.”

So saying, K opened that bag that was so ill-suited to his
shabby clothes and took out the head --- I didn't have time to
stop him.  I almost screamed.  It looked like an earthenware
head.  Once one looked at it, it was hard to look away.  It
was especially hard for me --- before my eyes was what remained
of the unforgettable face that made its ﬂight to see
me every night it was alive.

That, of course, is what my father did not tell Mr. K.  The
head of the beautiful Li ﬂew to my father every night.  The
ﬁrst time, he heard something like a bird brushing the
windowpane, and a sound like a kitten mewing sweetly.
Though my father spared me details I can imagine how they
conversed, when he'd let it in and stroked the chilled hair
strewn along the desktop.  I could not look my father in the
face while he was telling me this.  “Your mother never knew
about this.  I thought I should tell you someday, be-
cause, ....” My father hesitated.

“Let me finish with K first.  After K `killed' Li's head,
her body remained alive for several days.  Before it withered
and died, a baby girl was born from the headless body.  K
was arrested for raping and beheading his adopted daughter,
but he wasn't prosecuted because he was diagnosed to be
schizophrenic.  I adopted the girl and raised her as my own
daughter.  That's all I have to tell you.  I haven't dared ex-
amine you to see if you've inherited the disease."

After my father's sudden death, I repeated this story to
myself time and again.  For now I have no lover, nor have I
met one in a dream.  I don't think my head has yet begun to
ﬂy.  It shall not ﬂy --- until the day I fall in love.

\end{document}
